Radio Properties of Young Protostars in the Central Filament of the Serpens South Infrared Dark Cloud

### 2014-12-24 Paper/paper.tex
modified:   Data/reduction_notes.txt 	new file:   Dzib13_Classes.tab 	new file:   Dzib13_Classes_Corr.tab 	new file:   Dzib13_Data.tab 	new file:   Dzib13_Data_Corr.tab 	modified:   Make_Figs.py 	new file:   Mallick13_Data.tab 	new file:   Paper/figures/Infra_SEDs_OnePlot-eps-converted-to.pdf 	new file:   Paper/figures/SPIRE_350_Figure-eps-converted-to.pdf 	new file:   Paper/figures/SerpSouth_Lower_GaussFits-eps-converted-to.pdf 	new file:   Paper/figures/SerpSouth_PACS70_Contour-eps-converted-to.pdf 	new file:   Paper/figures/SerpSouth_SPIRE250_Contour-eps-converted-to.pdf 	new file:   Paper/

%% Begin Document
\begin{document}
%\submitted{Submitted: \today}
\title{Radio Sources in the Central Filament of the Serpens South Protocluster}
\author{Authors}

@@

We present 4.14 and 6.31 centimeter continuum observations of the Serpens South protocluster with the Karl G. Jansky Very Large Array in its C configuration. Our focus is a 3.5' x 3.5' area around the central filament. We detect roughly 18 sources, 10 of which are probably protostellar in nature. We characterize the radio emission and put it in context with 2MASS, Spitzer and Herschel data from the region. We find new embedded protostars that have yet to be resolved at shorter wavelengths, and in some cases confirm compact centimeter emission in previously identified starless cores. We compare our radio sources to the known centimeter vs. bolometric luminosity relationship. With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more protostars at centimeter wavelengths.

@@

	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation. Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}. X-ray studies of Serpens South have yet to be published. Presently only one radio study of Serpens South has been conducted, which used the Karl G. Jansky Very Large Array (VLA) in its A configuration in 2011 (Ortiz-Leon et al. in prep).

	Because of its isolated formation, Serpens South presents a unique opportunity to study the environmental influences on protostars in a young stellar cluster. A multi-wavelength approach will be key to fully understanding to non-normative behaviors of protostars in a high-density environment such as Serpens South.

	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}. Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components, thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. Free-free emission around low-mass protostars arises from shocks at the base of protostellar jets that shock the surrounding envelope material. Non-thermal emission around young (Class 0 and I), low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission created by stellar magnetic fields. (The gyrosynchrotron can also be magnetic reconnection events in their coronae I believe, check some of the recent Goulds Belt distance papers for their explanations.) %or possibly from jets that produce synchrotron emission in their tails.

	Towards the two goals of 1) locating new embedded protostars in the Serpens South protocluster and 2) better understanding the mechanisms of protostellar radio emission on a global scale, we carried out EVLA observations of Serpens South's central filament at 4.1 and 6.3 centimeters. In $\S 2$ we present our observations. In $\S 3$ we present our results. In $\S 4$ we discuss the implications of our study and in $\S 5$ we summarize our results.

@@

We observed Serpens South on July 2, 2013, for 1 hour with the EVLA in its C array configuration. The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband. We focused on a 3.5 arcmin x 3.5 arcmin region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$. The 6.31 and 4.14 cm images had primary beam diameters of 9.5 and 6.2 arcminutes respectively. Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation. \autoref{fig:serpsouth_fov} shows Serpens South at 350 micron and outlines our field of view.

\begin{figure}[h!]
\label{fig:serpsouth_fov}
\centering
\includegraphics[keepaspectratio=True,scale=.55]{figures/SerpSouth_FOV.eps}
\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South. Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively. The green box indicates our region of interest with the EVLA.}}
\end{figure}

We manually flagged, calibrated and imaged our data with standard procedures using Common Astronomy Software Applications (CASA) 4.1.0. We used J1331+305 (3C286) as a flux and bandpass calibrator, and J1804+0101 as a gain and phase calibrator ($S_{6.31\text{cm}}$ = 0.70 $\pm$ 0.02 Jy, $S_{4.14\text{cm}}$ = 0.66 $\pm$ 0.02 Jy). We deconvolved the Stokes $I$ images with the Cotton-Schwab algorithm \citep{Schwab84} using the CLEAN method \citep{Hogbom74,Clark80}. We experimented with natural, robust and uniform weighting, and found the best compromise between noise level and source resolution with robust weighting, also known as Briggs weighting \citep{Briggs95}, with a \emph{robust} parameter set to 0.5. The synthesized beam sizes and RMS values for our two images are detailed in \autoref{tab:image_pars}.

Observing Serpens South at radio wavelengths is difficult because of the extended and bright HII region W40 directly to the East, which adds to over-resolved flux and increases the RMS noise level in our images. In addition, our short integration time--45 minutes on source--left us with a less than desirable UV coverage at long UV distances. Long UV distance coverage is particularly important because we are trying to resolve point source emission. Further EVLA studies of Serpens South would benefit from extended array configurations and longer integration times.

@@

VLA\_1	&	18 30 09.68	&	-02 00 32.8	&	749 $\pm$ 6	&	718	&	844 $\pm$ 8	&	794	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02	&	Extragal.?\\[1ex]

VLA\_2	&	18 30 04.79	&	-02 00 34.1	&	177 $\pm$ 7	&	138	&	87 $\pm$ 7	&	72	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14	&	Extragal.\\[1ex]

VLA\_3	&	18 30 02.55	&	-02 00 48.5	&	140 $\pm$ 2	&	99	&	116 $\pm$ 10	&	87	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15	&	Extragal.\\[1ex]

VLA\_4	&	18 30 01.53	&	-02 00 51.6	&	1663 $\pm$ 32	&	1178	&	946 $\pm$ 28	&	515	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02	&	Extragal.\\[1ex]

VLA\_5	&	18 30 14.79	&	-02 01 27.3	&	106 $\pm$ 5	&	95	&	167 $\pm$ 10	&	173	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13	&	Extragal.?\\[1ex]

VLA\_6	&	18 30 06.62	&	-02 01 28.9	&	79 $\pm$ 7	&	61	&	33 $\pm$ 4	&	56	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23	&	Extragal.\\[1ex]

VLA\_7	&	18 30 05.81	&	-02 01 44.9	&	48 $\pm$ 4	&	40	&	84 $\pm$ 7	&	63	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31	&	Class I\\[1ex]

VLA\_8	&	18 30 06.89	&	-02 02 11.5	&	39 $\pm$ 3	&	46	&	50 $\pm$ 6	&	50	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29	&	Extragal.?\\[1ex]

VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 1	&	50	&	60 $\pm$ 1	&	44	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29	&	Class 0?\\[1ex]

VLA\_10	&	18 30 02.95	&	-02 02 32.2	&	287 $\pm$ 6	&	119	&	260 $\pm$ 17	&	73	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15	&	Unknown\\[1ex]

VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 2	&	36	&	73 $\pm$ 4	&	58	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]

VLA\_12	&	18 30 04.11	&	-02 03 02.1	&	30 $\pm$ 2	&	24	&	79 $\pm$ 2	&	58	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48	&	Class 0$^{*}$\\[1ex]

VLA\_13	&	18 30 03.54	&	-02 03 08.4	&	186 $\pm$ 1	&	178	&	231 $\pm$ 3	&	227	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07	&	Class 0$^{*}$\\[1ex]

VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 0	&	37	&	83 $\pm$ 2	&	61	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]

VLA\_15	&	18 30 04.60	&	-02 03 14.1	&	68 $\pm$ 1	&	52	&	49 $\pm$ 4	&	51	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27	&	Extragal.\\[1ex]

VLA\_16	&	18 30 03.25	&	-02 03 26.6	&	63 $\pm$ 2	&	58	&	55 $\pm$ 1	&	65	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23	&	Class II\\[1ex]

VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 3	&	135	&	161 $\pm$ 4	&	167	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1	&	Class I\\[1ex]

VLA\_18	&	18 30 09.40	&	-02 04 08.8	&	170 $\pm$ 3	&	182	&	167 $\pm$ 10	&	134	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09	&	Extragal.?

\enddata
\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\tablenotetext{c}{Spectral index of integrated flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
\tablenotetext{d}{Spectral index of peak flux from 6.3 to 4.1 cm.}
\tablenotetext{e}{Classification of source. Unless otherwise noted, Class 0 classifications come from Herschel \citep{Bontemps10} and Class I \& II  from Spitzer \citep{Gutermuth08}. (?) denotes uncertaintity. ($^{*}$) denotes classified by this work.}

@@

In choosing our sources, we restricted ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength. We chose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}. We took only sources that had at least a $4\sigma$ strength in the 4.1 cm image, and were left with a total of 18 radio sources. We note that we found $\sim$6 sources at the $2\sigma$ level that aligned within 2 arcsecond of an infrared association, however, we do not consider them strong detections and do not include them in our final source list. As stated in \autoref{sec:observations}, further observations with longer integration will likely be able to confidently detect these protostellar radio sources.

\begin{figure}[h!]
\label{fig:serpsouth_fov_contour}
\centering
\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
\caption{\small{Serpens South radio continuum at 6.3 cm, focused in on green box from \autoref{fig:serpsouth_fov}. Radio contours start at 4$\sigma$ and end at 50$\sigma$. The loose black contour is the same SPIRE 350 $\mu$m contour found in \autoref{fig:serpsouth_fov}. 
}}
\end{figure}

\begin{figure*}
\label{fig:zoom}
\epsscale{1.15}

\plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
\caption{{\bfseries Left}: Radio continuum at 6.3 cm focused in on red box from \autoref{fig:serpsouth_fov_contour}. Blue and red crosses correspond to Spitzer identified Class I and II protostars. Green crosses correspond to 1.2 mm dust peaks identified by IRAM. {\bfseries Right}: Identical contours on the left but with a background PACS 70 $\mu$m image. The radio contour beam size is shown to the lower-left.}
\end{figure*}

We ran source extractions on the spatial positions of our final source list over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel. We used a 2 arcsecond maximum matching tolerance for these extractions. Apertures and adopted corrections were consistent with the HOPS survey.

Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match Spitzer identified Class I/II protostars within 1 arcsecond. A total of ten out of our 18 sources have signs that indicate they are protostellar in nature. One of our radio sources, VLA 12, matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they quote as starless.

We can calculate the number of random background sources we would expect to find in our images. We use the formulation found in \citet{Shirley07}, who draw from radio studies done by \citet{Fomalont91}. The density of random background radio sources above a flux limit of $S\ \mu$Jy at 6 cm is given by $N(>S) = 0.42\cdot(S/30\ \mu \text{Jy})^{-1.18}$ arcmin$^{-2}$. Therefore, the total number of sources with flux $S$ greater than 50 $\mu$Jy at 6 cm is 0.229 arcmin$^{-2}$. This leads to a 0.4\% chance that a background source falls inside any one synthesized beam centered on a compact radio source, and gives us on average $\sim$9 background sources above 50 $\mu$Jy within our 3.5' x 3.5' region of interest. This agrees with our analysis, as we find roughly 8 sources that are likely background sources.

%\subsection{Spectral Indices}
%\label{sec:spix}
%A spectral index is the slope of the flux density in log space between two wavelengths. At radio wavelengths, the spectral index is defined as
%
%\begin{equation}
%\label{eq:radio_spix}
%\alpha_{\text{radio}} = \frac{\ln({S_{\lambda_{1}}/S_{\lambda_{2}})}}{\ln({\lambda_{2}/\lambda_{1}})}
%\end{equation}
%where $\lambda_{2} > \lambda_{1}$ \citep{Shirley07}. Note that we have defined $S_{\lambda}$ in terms of a flux density (e.g. Jansky) not a flux (e.g. $\lambda S_{\lambda}$ or $\nu S_{\nu}$). Theoretical studies have shown that 
%

@@

\sourcenote{Extragalactic Sources}
VLA 2, 3, 4, 6, and 15 are very likely extragalactic in nature. They have no visible associations from 1$\mu$m to 70$\mu$m and have negative radio spectral indices indicative of non-thermal synchrotron emission.

\sourcenote{Unclear Sources}
While VLA 1 and 5 have no infrared, far-infrared or millimeter associations and are isolated from the filament, they have a flat and rising radio spectral indices suggesting optically thin and thick free-free emission respectively. Although galaxies can produce free-free emission from large HII clouds, the dominant component of a galaxy's radio emission output comes from non-thermal synchrotron emission with a declining spectrum. Nonetheless, we tentatively classify these sources as extragalactic due to their lack of associations.

VLA 18 is spatially distinct from the filament but has a flat radio spectral index and actually has three very weak infrared associations at 3.6, 4.5 and 5.8 $\mu$m. However, we speculate that these associations are coincidental and tentatively classify VLA 18 as extragalactic.

>>>>

%% Begin Document
\begin{document}
%\submitted{Submitted: \today}
\title{Radio Properties of Young Protostars in the Central Filament of the Serpens South Infrared Dark Cloud}
\author{Authors}

@@

We present 4.14 and 6.31 centimeter continuum observations of the Serpens South protocluster with the Karl G. Jansky Very Large Array in its C configuration. Our focus is a 3.5' x 3.5' area around the central filament. We detect roughly 18 sources, 10 of which are probably protostellar in nature. We characterize the radio emission and put it in context with 2MASS, Spitzer and Herschel data from the region. We compare our radio sources to the known centimeter vs. bolometric luminosity relationship. With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more protostars at centimeter wavelengths. [Not finished...]

@@

	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy Survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation.

	Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14, Nakamura14a}. X-ray studies of Serpens South have yet to be published. Presently only one radio study of Serpens South has been conducted, which used the Karl G. Jansky Very Large Array (VLA) in its A configuration in 2011 (Ortiz-Leon et al. in prep).

%	Because of its isolated formation, Serpens South presents a unique opportunity to study the environmental influences on protostars in a young stellar cluster. A multi-wavelength approach will be key to fully understanding to non-normative behaviors of protostars in a high-density environment such as Serpens South.

	Early radio studies of protostars found an excess of radio emission compared to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components, thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. Free-free emission around low-mass protostars arises from shocks at the base of protostellar jets that shock the surrounding envelope material. Non-thermal emission around young (Class 0 and I), low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission created by stellar magnetic fields. (The gyrosynchrotron can also be magnetic reconnection events in their coronae I believe, check some of the recent Goulds Belt distance papers for their explanations.) %or possibly from jets that produce synchrotron emission in their tails.

	The VLA has been a proven tool for detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10,Dzib13}. With the goal of locating embedded protostars in the Serpens South protocluster, we carried out VLA observations of Serpens South's central filament at 4.1 and 6.3 centimeters. In $\S 2$ we present our observations. In $\S 3$ we present our results. In $\S 4$ we discuss the implications of our study and in $\S 5$ we summarize our results.

@@

We observed Serpens South on July 2, 2013, for 1 hour with the VLA in its C array configuration. In order to derive a spectral index, we split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm) with a bandwidths of 1.024 GHz. At 4.75 and 7.25 GHz, our images had primary beam diameters of 9.5 and 6.2 arcminutes respectively. Our observation focused on a 3.5 arcmin x 3.5 arcmin region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$ (\autoref{fig:serpsouth_fov}). During our hour-long observation, we switched from Serpens South to J1804 + 0101 every 10 minutes for gain calibrations.

\begin{figure}[h!]
\label{fig:serpsouth_fov}
\centering
\includegraphics[keepaspectratio=True,scale=.55]{figures/SerpSouth_FOV.eps}
\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South outlining its filamentary structure. Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively. The green box indicates our region of interest with the VLA. The black contour intensity level is set at 365 mJy/sr.}}
\end{figure}

We manually flagged, calibrated and imaged our data with standard procedures using Common Astronomy Software Applications (CASA) 4.1.0. We used J1331+305 (3C286) as a flux and bandpass calibrator, and J1804+0101 as a gain and phase calibrator ($S_{6.31\text{cm}}$ = 0.70 $\pm$ 0.02 Jy, $S_{4.14\text{cm}}$ = 0.66 $\pm$ 0.02 Jy). We deconvolved the Stokes $I$ images with the Cotton-Schwab algorithm \citep{Schwab84} using the CLEAN method \citep{Hogbom74,Clark80}. We experimented with natural, robust and uniform weighting, and found the best compromise between noise level and source resolution using robust weighting \citep{Briggs95}, with the \emph{robust} parameter set to 0.5. The synthesized beam sizes and RMS values for our two images are detailed in \autoref{tab:image_pars}. We performed a primary beam correction on our images by convolving the CLEANed images with the array's modeled flux response.

%Observing Serpens South at radio wavelengths is difficult because of the extended and bright HII region W40 directly to the East, which adds to over-resolved flux and increases the RMS noise level in our images. In addition, our short integration time--45 minutes on source--left us with a less than desirable UV coverage at long UV distances. Long UV distance coverage is particularly important because we are trying to resolve point source emission. Further VLA studies of Serpens South would benefit from extended array configurations and longer integration times.

@@

VLA\_1	&	18 30 09.68	&	-02 00 32.8	&	749 $\pm$ 42	&	718	&	844 $\pm$ 43	&	794	&	0.28 $\pm$ 0.08	&	0.24 $\pm$ 0.07	&	Extragal.?\\[1ex]

VLA\_2	&	18 30 04.79	&	-02 00 34.1	&	177 $\pm$ 5	&	138	&	87 $\pm$ 8	&	72	&	-1.67 $\pm$ 0.1	&	-1.55 $\pm$ 0.16	&	Extragal.\\[1ex]

VLA\_3	&	18 30 02.55	&	-02 00 48.5	&	140 $\pm$ 6	&	99	&	116 $\pm$ 12	&	87	&	-0.46 $\pm$ 0.11	&	-0.3 $\pm$ 0.16	&	Extragal.\\[1ex]

VLA\_4	&	18 30 01.53	&	-02 00 51.6	&	1663 $\pm$ 50	&	1178	&	946 $\pm$ 55	&	515	&	-1.33 $\pm$ 0.07	&	-1.96 $\pm$ 0.07	&	Extragal.\\[1ex]

VLA\_5	&	18 30 14.79	&	-02 01 27.3	&	106 $\pm$ 12	&	95	&	167 $\pm$ 13	&	173	&	1.07 $\pm$ 0.14	&	1.41 $\pm$ 0.14	&	Extragal.?\\[1ex]

VLA\_6	&	18 30 06.62	&	-02 01 28.9	&	79 $\pm$ 3	&	61	&	33 $\pm$ 4	&	56	&	-2.04 $\pm$ 0.15	&	-0.22 $\pm$ 0.24	&	Extragal.\\[1ex]

VLA\_7	&	18 30 05.81	&	-02 01 44.9	&	48 $\pm$ 8	&	40	&	84 $\pm$ 8	&	63	&	1.29 $\pm$ 0.2	&	1.08 $\pm$ 0.31	&	Class I\\[1ex]

VLA\_8	&	18 30 06.89	&	-02 02 11.5	&	39 $\pm$ 5	&	46	&	50 $\pm$ 6	&	50	&	0.55 $\pm$ 0.19	&	0.18 $\pm$ 0.3	&	Extragal.?\\[1ex]

VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 3	&	50	&	60 $\pm$ 3	&	44	&	-0.22 $\pm$ 0.07	&	-0.31 $\pm$ 0.3	&	Class 0$^{*}$?\\[1ex]

VLA\_10	&	18 30 02.95	&	-02 02 32.2	&	287 $\pm$ 14	&	119	&	260 $\pm$ 21	&	73	&	-0.23 $\pm$ 0.1	&	-1.15 $\pm$ 0.16	&	Unknown\\[1ex]

VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 6	&	36	&	73 $\pm$ 5	&	58	&	1.5 $\pm$ 0.17	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]

VLA\_12	&	18 30 04.11	&	-02 03 02.1	&	30 $\pm$ 8	&	24	&	79 $\pm$ 4	&	58	&	2.31 $\pm$ 0.27	&	2.06 $\pm$ 0.48	&	Class 0\\[1ex]

VLA\_13	&	18 30 03.54	&	-02 03 08.4	&	186 $\pm$ 11	&	178	&	231 $\pm$ 12	&	227	&	0.51 $\pm$ 0.08	&	0.58 $\pm$ 0.1	&	Class 0\\[1ex]

VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 4	&	37	&	83 $\pm$ 4	&	61	&	2.29 $\pm$ 0.15	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]

VLA\_15	&	18 30 04.60	&	-02 03 14.1	&	68 $\pm$ 2	&	52	&	49 $\pm$ 4	&	51	&	-0.74 $\pm$ 0.1	&	-0.08 $\pm$ 0.28	&	Extragal.\\[1ex]

VLA\_16	&	18 30 03.25	&	-02 03 26.6	&	63 $\pm$ 3	&	58	&	55 $\pm$ 3	&	65	&	-0.28 $\pm$ 0.08	&	0.27 $\pm$ 0.24	&	Class II\\[1ex]

VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 8	&	135	&	161 $\pm$ 9	&	167	&	0.22 $\pm$ 0.08	&	0.5 $\pm$ 0.12	&	Class I\\[1ex]

VLA\_18	&	18 30 09.40	&	-02 04 08.8	&	170 $\pm$ 9	&	182	&	167 $\pm$ 13	&	134	&	-0.04 $\pm$ 0.1	&	-0.71 $\pm$ 0.11	&	Extragal.?

\enddata
\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\tablenotetext{c}{Spectral index of integrated flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
\tablenotetext{d}{Spectral index of peak flux from 6.3 to 4.1 cm.}
\tablenotetext{e}{Classification of source. Unless otherwise noted, Class 0 classifications come from Herschel \citep{Bontemps10} and Class I \& II  from Spitzer \citep{Gutermuth08}. (?) denotes uncertainty. ($^{*}$) denotes classified by this work.}

@@

Out of the 50+ Spitzer identified Class I and II YSOs located in and around Serpens South's central filament, we detect 18 radio sources at our sensitivity level. In choosing our sources, we restricted ourselves to a circular region centered on our phase center extending out to 50\% of the primary beam response. We chose our sources based on their appearance and strength in both our 4.1 and 6.3 cm images, their spatial proximity to infrared associations, and by referencing a source extracted sample using Sextractor \citep{Bertin96}. We only took sources that had at least a $4\sigma$ detection in the 4.1 cm image. We note that we found $\sim$6 sources at the $2\sigma$ level that aligned within 2 arcsecond of infrared associations, however, we do not consider them strong detections and do not include them in our final source list. Further observations with higher sensitivity will likely be able to confidently detect these protostellar radio sources.

\begin{figure}
\label{fig:serpsouth_fov_contour}
\centering
\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
\caption{\small{Serpens South's central filament at 4.1 cm, focused in on the green box from \autoref{fig:serpsouth_fov}. Radio contours start at 4$\sigma$ and end at 50$\sigma$. The loose black contour is the same SPIRE 350 $\mu$m contour found in \autoref{fig:serpsouth_fov}. 
}}
\end{figure}

\begin{figure*}
\label{fig:zoom}
\epsscale{1.15}
\plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
\caption{{\bfseries Left}: Radio continuum of our sources VLA 6 to VLA 17 at 4.1 cm. Blue and red crosses correspond to Class I and II protostars, respectively, identified by Spitzer. Green crosses correspond to 1.2 mm dust peaks identified by IRAM. {\bfseries Right}: Identical contours on the left but with a background PACS 70 $\mu$m image. The radio image beam size is shown to the lower-left.}
\end{figure*}

We used CASA's IMFIT function to fit 2D gaussians to our chosen radio sources. For strong and relatively isolated sources, we can reasonably rely on the 2D gaussian integrated flux densities. For somewhat blended sources, such as VLA 9 and 14, manually-calculated peak fluxes are likely more reliable for spectral index calculations. Integrated flux errors were calculated by adding in quadrature the flux error output from IMFIT with an assumed 5\% systematic flux calibration error. Peak flux errors were calculated by adding in quadrature the relative error of the image RMS with an assumed 5\% systematic flux calibration error.

We cross-referenced our radio source positions with the 2MASS catalogue, and ran source extractions over the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel. We used a 2 arcsecond maximum matching tolerance for these extractions. Apertures and adopted corrections were consistent with the HOPS survey (Gutermuth et al. in prep).

Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match a Spitzer identified Class I or II protostar within 1 arcsecond. A total of ten out of our 18 sources have signs that indicate they are protostellar in nature. One of our radio sources, VLA 12, matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they identify as Class 0.

We can calculate the number of random background sources we would expect to find in our images. We use the formulation found in \citet{Shirley07} and \citet{Dzib13}, who draw from radio studies done by \citet{Fomalont91}. The density of random background radio sources above a flux limit of $S\ \mu$Jy at 6 cm is given by 
\begin{equation*}
n(>S) = 0.42\pm0.05\left(\frac{S}{30\ \mu \text{Jy}}\right)^{-1.18\pm0.19} \text{arcmin}^{-2}
\end{equation*}
Therefore, the total number of sources with flux $S$ greater than 30 $\mu$Jy at 6 cm is 0.42 arcmin$^{-2}$. This leads to a 0.7\% chance that a background source falls inside a 4.8 x 3.9 arcsec synthesized beam centered on a compact radio source. It also gives us on average $\sim6\pm1$ background sources within our 3.5' x 3.5' region of interest above a 3$\sigma$ level. We find roughly 5 to 8 sources that we identify as extragalactic, which is at worst within 2 standard deviations from the expectation.

\subsection{Spectral Indices}
\label{sec:spix}
At radio wavelengths, the spectral index is defined as
\begin{equation}
\label{eq:radio_spix}
\alpha_{\text{radio}} = \frac{\ln({S_{\lambda_{1}}/S_{\lambda_{2}})}}{\ln({\lambda_{2}/\lambda_{1}})}
\end{equation}
where $\lambda_{2} > \lambda_{1}$ \citep{Shirley07}. Note that we have defined $S_{\lambda}$ in terms of a flux density (e.g. Jansky) and not a flux (e.g. $\lambda S_{\lambda}$ or $\nu S_{\nu}$). Flat radio spectral indices ($\alpha > -0.1$) are generally indicative of optically thin free-free emission, while rising indices ($\alpha \sim 2.0$) are representative of optically thick free-free emission \citep{Anglada98}.

@@

\sourcenote{Extragalactic Sources}
VLA 2, 3, 4, 6, and 15 are very likely extragalactic in nature. They have no visible associations from 1$\mu$m to 70$\mu$m and have negative radio spectral indices indicative of non-thermal synchrotron emission typical of a galaxy's radio spectrum.

\sourcenote{Unclear Sources}
While VLA 1 and 5 have no infrared, far-infrared or millimeter associations and are isolated from the filament, they have a flat or rising radio spectral indices suggesting optically thin or thick free-free emission respectively. Although galaxies can produce free-free emission from large HII clouds, the dominant component of a galaxy's radio emission output comes from non-thermal synchrotron emission with a declining spectrum. Moreover, in \citet{Dzib13}'s study of 190 radio sources in the Ophiuchus star forming cloud, they didn't find a single extragalactic source with a radio spectral index larger than $\sim$0. Nonetheless, we tentatively classify these sources as extragalactic due to their lack of any association at shorter wavelengths.

VLA 18 is spatially distinct from the filament but has a flat radio spectral index and actually has three very weak infrared associations at 3.6, 4.5 and 5.8 $\mu$m. However, we speculate that these associations are coincidental due to their odd linear behavior, and tentatively classify VLA 18 as extragalactic.
